### 2015-07-10 abstract.tex

Our objective here is to reduce the time to knowledge, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond 
checkpoint/restart I/O, and will address the challenges posed by 
key
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future Department of Energy (DOE) system with many of today's applications, including the
XGC1, GTC, QMCPack, and SpecFM3D simulations. 
Our solutions will provide  new functionalities and Application Program Interfaces (API) for:
1) specifying, at the application level, data annotations that enable the
quantification of the relative importance and utility of data objects and
enable partitioning  across the storage hierarchy;
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives;
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continuous learning; and
4) leveraging techniques such as application-aware data compression, 
and I/O prioritization to enforce these
policies.
\noindent

>>>>

Our objective here is to reduce the time to knowledge, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond 
checkpoint/restart I/O, and will address the challenges posed by 
key
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future Department of Energy (DOE) system with many of today's applications, including the
XGC1, GTC, QMCPack, and SpecFM3D simulations. 
Our solutions will provide  new functionalities and Application Program Interfaces (API) for:
1) specifying, at the application level, data annotations that enable the
quantification of the relative importance and utility of data objects and
enable partitioning  across the storage hierarchy;
2) specifying selectable performance/quality/cost tradeoffs from both the
application and system perspectives;
3) evaluating these tradeoffs at runtime during data placement and movement,
and executing the resultant policies in an autonomic system using models,
heuristics and continuous learning; and
4) leveraging techniques such as application-aware data compression, 
and  I/O utility to enforce these
policies.
\noindent

### 2015-07-10 narrative/intro.tex

One of our research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Central to our approach is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds, and furthermore, with optimizations we would like to minimize 
the times for both reading and writing. Thus, we want predictable performance, and methods
which can obtain better performance bounds in time. Furthermore, since our system will place chunks
in all of the tiers  we need to quickly discover where the data is in the hierarchy~\S\ref{sec:naming-discovery}

>>>>

One of our research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
Central to our approach is that the storage system needs to define bounds of time estimates
(min time, max time), and as our system evolves, we want to allow plug-ins which can help
reduce the range of the bounds.
Overall, our goal is to enable predictable performance acorss the storage system, and we will develop mechanisms to enable this
~\S\ref{sec:naming-discovery}.
